\LARGE \bf Enriching Robot's Actions with Affective Movements

### 2017-06-11 RO-MAN-2017-2/Parts/EmotionalTree.tex
Reviewed

\subsection{Formalization of Simple and Compound Actions}
Formalizing simple and compound actions enables the generation of a system to design them and verify if they are described correctly. Simple actions ($SA$) could be seen as functions that map a set of parameters $p^{pl}_{i} \in P$ to specific platform ($pl$) movements ($m^{pl}_{j}\in M^{pl}$) in the set of movements for that platform ($m^{pl}_{j} =sa^{pl}(\lbrace p^{pl}_{i} \rbrace)$). Each $sa^{pl}$ could have different implementations due to different reasons such as: platform's configuration, action's goal, how the mapping from inputs to outputs are done, among others. 
In our case, we consider that two actions are different if $(\forall sa_{i}, sa_{j} \in SA, \forall q, t \in PL | Param( sa_{i}^q ) \neq Param( sa_{j}^t )\Rightarrow sa_{i}^q \neq sa_{j}^t)$, 
where $PL$ is the set of all the possible platforms, $Param(\cdot)$ returns the set of parameters that are input of the $sa$ (e.g., $vel$,$pitch$,$text$). 
On the other hand, we will consider two actions as equivalents if $(\forall sa_{i}, sa_{j} \in SA , \forall q, t \in PL | Param( sa_{i}^q ) = Param(sa_{j}^t ) \wedge Obj(sa_{i}^q) = Obj(sa_{j}^t) \Rightarrow sa_{i}^q \equiv sa_{j}^t)$,  
where $Obj(\cdot)$ returns the set of objectives that are intended to be achieved by a given action. This $SA$ equivalence allows us to avoid the specification of all the platforms for all the actions that share the same objective and hide leaf nodes that do not give relevant information to understand the emotional tree.

With this $SA$ definition, it is now possible to define emotion enrichment as $ (\forall sa \in SA, \forall e \in E, \exists \; en$ $|$ $en=Enrichment(sa,e,Param(sa), Intensity(e)))$, where $Intensity(\cdot)$ returns the intensity of a given emotion, $E$ is the set of emotions, and $en$ can be the same $sa$, but with the parameters modified in order to convey the desired emotion $e$, or even a set of $sa$ with modified parameters. This definition goes along with the idea that new $sa$ could be added to convey a specific emotion. In addition, the $Enrichment(\cdot)$ function has the following properties:
\begin{itemize}
	\item $(\forall sa_{i},sa_{j} \in SA, \forall e \in E$ $|$ $sa_{i} \equiv sa_{j} \Rightarrow Enrichment(sa_{i},e,...) \equiv Enrichment(sa_{j},e,...))$
	\item $(\forall sa_{i},sa_{j} \in SA, \forall e \in E$ $|$ $(sa_{i} \not\equiv sa_{j}) \Rightarrow Enrichment(sa_{i},e,...) \not \equiv Enrichment(sa_{j},e,...))$
\end{itemize}

>>>>

\subsection{Formalization of Simple and Compound Actions}
Formalizing simple and compound actions enables the generation of a system to design them and verify if they are described correctly. Simple actions ($SA$) could be seen as functions that map a set of parameters $p^{pl}_{i} \in P$ to specific platform ($pl$) movements ($m^{pl}_{j}\in M^{pl}$) in the set of movements for that platform ($m^{pl}_{j} =sa^{pl}(\lbrace p^{pl}_{i} \rbrace)$). Each $sa^{pl}$ could have different implementations due to different reasons such as: platform's configuration, action's goal, how the mapping from inputs to outputs are done, among others. 
In our case, we consider that two actions are different if $(\forall sa_{i}, sa_{j} \in SA, \forall q, t \in PL | Param( sa_{i}^q ) \neq Param( sa_{j}^t )\Rightarrow sa_{i}^q \neq sa_{j}^t)$, 
where $PL$ is the set of all the possible platforms, $Param(\cdot)$ returns the set of parameters that are input of the $sa$ (e.g., $vel$, $pitch$, $text$). 
On the other hand, we will consider two actions as equivalent if $(\forall sa_{i}, sa_{j} \in SA , \forall q, t \in PL | Param( sa_{i}^q ) = Param(sa_{j}^t ) \wedge Obj(sa_{i}^q) = Obj(sa_{j}^t) \Rightarrow sa_{i}^q \equiv sa_{j}^t)$,  
where $Obj(\cdot)$ returns the set of objectives that are intended to be achieved by a given action. This $SA$ equivalence allows us to avoid the specification of all the platforms for all the actions that share the same objective and hide leaf nodes that do not give relevant information to understand the emotional tree.

With this $SA$ definition, it is now possible to define emotion enrichment as $ (\forall sa \in SA, \forall e \in E, \exists \; en$ $|$ $en=Enrichment(sa,e,Param(sa), Intensity(e)))$, where $Intensity(\cdot)$ returns the intensity of a given emotion, $E$ is the set of emotions, and $en$ can be the same $sa$, but with modified parameters in order to express the desired emotion $e$, or even a set of $sa$ with modified parameters. This definition goes along with the idea that new $sa$ could be added to convey a specific emotion. In addition, the $Enrichment(\cdot)$ function has the following properties:
\begin{itemize}
	\item $(\forall sa_{i},sa_{j} \in SA, \forall e \in E$ $|$ $sa_{i} \equiv sa_{j} \Rightarrow Enrichment(sa_{i},e,...) \equiv Enrichment(sa_{j},e,...))$
	\item $(\forall sa_{i},sa_{j} \in SA, \forall e \in E$ $|$ $(sa_{i} \not\equiv sa_{j}) \Rightarrow Enrichment(sa_{i},e,...) \not \equiv Enrichment(sa_{j},e,...))$
\end{itemize}
